\documentclass[12pt]{article}

\pagestyle{empty}
\setcounter{secnumdepth}{0}

\topmargin=0cm
\oddsidemargin=0cm
\textheight=22.0cm
\textwidth=16cm
\parindent=0cm
\parskip=0.15cm
\topskip=0truecm
\raggedbottom
\abovedisplayskip=3mm
\belowdisplayskip=3mm
\abovedisplayshortskip=0mm
\belowdisplayshortskip=2mm
\normalbaselineskip=12pt
\normalbaselines

\begin{document}

\vspace*{0.2in}
\centerline{\bf\Large Diary}

\vspace*{0.2in}
\centerline{\bf\Large Name: Tiffany Ah King  Student ID: 40082976}

\vspace*{0.2in}
\centerline{\bf\Large Team PK-A}

\vspace*{0.2in}
\centerline{\bf\Large 09 February 2020}

\section{Iteration 1}

{\bf Date:} 09 January 2020\\
{\bf Start Time:} 20:15\\
{\bf End Time:} 21:00 \\
{\bf Who:} Tiffany Ah King, Isabelle Charette, Brian Gamboc-Javiniar, Vsevolod Ivanov,
Chang Liu, Nolan Mckay, Nalveer Moocheet, Hoang Thuan Pham, Audrey-Laure St-Louis, Jia Ming Wei\\
{\bf Where:} H-920 \\
{\bf Activities:} We introduced each other and learned our interests and motivation. We talked about what are expected from everyone which are honesty, respect and hardwork. Then, we determined and created platforms for communications. We took note of everyone's emails.\\
{\bf Outcomes:} For communnication, we have chosen Discord which I created a server later on and added everyone. For programming, it was GitHub where Vsevold Ivanov created a repository. Jia Ming created the Then, we fixed the next meeting at the lab Wednesday. Total time of this week: 3 hours.\\ \\


{\bf Date:} 12 January 2020\\
{\bf Start Time:} 2:30\\
{\bf End Time:} 3:00  \\
{\bf Who:} Tiffany Ah King\\
{\bf Where:} Home \\
{\bf Activities:}I went through the project description to be informed on what to do for our first lab.\\
{\bf Outcomes:} I created an agenda and posted it on Discord so as everyone know what we will do.\\ \\

{\bf Date:} 15 January 2020\\
{\bf Start Time:} 19:15 \\
{\bf End Time:} 21:00 \\
{\bf Who:}  Tiffany Ah King, Isabelle Charette, Brian Gamboc-Javiniar, Vsevolod Ivanov,
Chang Liu, Nolan Mckay, Nalveer Moocheet, Hoang Thuan Pham, Audrey-Laure St-Louis, Jia Ming Wei \\
{\bf Where:} H831 \\
{\bf Activities:} The tutor, Mohammad Reza Rejali, covered the "programming cycle" - Planning, Analysis, Design, Implementation and Maintenance. He introduced us to the difference of the lecture, tutorial and lab and their importance. He talked about the goal of a software, its problems, its solutions and its benefits. The tutor explained and went over the project description, about the demo and the diffent roles (Coder, Documenter, Organizer).\\

Then, team PK-A discussed about who will do what for Iteration. There will be 3  coders, 5 documenters, 1 QA and 1 organizer. \\

Coders: Isabelle Charette, Nalveer Moocheet and Vsevolod Ivanov\\

Documenters: Tiffany Ah King, Chang Liu, Brian Gamboc-Javiniar, Nolan Mckay and  Hoang Thuan Pham\\

Organizer: Jia Ming Wei\\

Quality Control: Audrey-Laure St-Louis\\

As a team, we discussed about the different user cases and we came up with five. Each coder and documenter have each one user case to take care of for Iteration 1. 
\\

{\bf Outcomes:} Everyone in the group got a role and we were aware of the test cases. We all had flexible tasks to explore before the next meeting. We started to think in terms of MVC for the structure of the code and of the documentation. We exchanged schedules through Discord\\\\

{\bf Date:} 16 January 2020\\
{\bf Start Time:} 20:30\\
{\bf End Time:} 21:20\\
{\bf Who:} Tiffany Ah King, Brian Gamboc-Javiniar,\\
 Hoang Thuan Pham, Jia Ming Wei\\
{\bf Where:} H-523\\
{\bf Activities:} During the tutorial, the TA explained more about the user stories and user diagram and gave us an example of the bank.\\
{\bf Outcomes:}In group, we came up with different user cases and we agreed to share our findings on Discord. Total time of this week: 6 hours.\\ \\

{\bf Date:} 22 January 2020\\
{\bf Start Time:} 14:00\\
{\bf End Time:} 16:00\\
{\bf Who:} Tiffany Ah King\\
{\bf Where:} Home\\
{\bf Activities:} I read and learned more about LaTex through Overleaf and the sample Latex template for the use case document. I skimmed over the "Monopoly Project Analysis and Development Plan Version 1.3" LaTex pdf that the professor, Greg Butler posted on his site. It was very resourceful and it helped me to have a headstart on the documentation. Futhermore, I documented myself on the Kakuro game and went on several websites like wikipedia among others.\\
{\bf Outcomes:} I wrote the title cover, the table of content, the introduction and try to make it have a good alignment.I had a problem with the date appearing at the top each time and I was able to resolve it. I used the LaTeX Base online to start with.\\ \\

{\bf Date:} 22 January 2020\\
{\bf Start Time:} 19:15\\
{\bf End Time:} 20:45\\
{\bf Who:} Tiffany Ah King, Isabelle Charette, Brian Gamboc-Javiniar, Vsevolod Ivanov,\\
Chang Liu, Nolan Mckay, Nalveer Moocheet, Hoang Thuan Pham, Audrey-Laure St-Louis, Jia Ming Wei\\
{\bf Where:} H-831\\
{\bf Activities:} We updated our work on where we were at that moment. The documenters were supposed to learned LaTex and to review  the user cases. Everyone tried to clear some confusion and misunderstandings and shed light on the implementation details. We also discussed about the upcomming demo lab of the Proof of Concept (PoC) which will be held on Wednesday 29 January in H831 at 19h15.\\
{\bf Outcomes:} Some misunderstanding were cleared. The documenters have decided to use google drive to share the work and the outline of what we are doing.The coders and documenters have their own discussion on their parts. The documentation group including me decided who will do what for the "Requirement Document" for Iteration1 . I am in charge of the title page, the introduction, the table of content, the references and the game mechanics because I already started it. We agreed to do a voice call over Discord on Sunday 26 January at 19h00. \\ \\ 

{\bf Date:} 26 January 2020\\
{\bf Start Time:} 19:00\\
{\bf End Time:} 20:00\\
{\bf Who:} Tiffany Ah King, Brian Gamboc-Javiniar,
Chang Liu, Nolan Mckay, Hoang Thuan Pham\\
{\bf Where:} Home via Discord Voice call\\
{\bf Activities:} We cleared any confusion and discussed about the merging which will happen on Tuesday and the demo on Wednesday 29 January. Additionally, we streamed on some user case diagram and what changes must be made.\\
{\bf Outcomes:} Everyone is on the same page and knows that they need to finish their parts before the merge and to get ready for the demo. Total time of this week: 10 hours.\\

{\bf Date:} 29 January 2020\\
{\bf Start Time:} 19:15\\
{\bf End Time:} 20:45\\
{\bf Who:} Tiffany Ah King, Isabelle Charette, Brian Gamboc-Javiniar, Vsevolod Ivanov,
Chang Liu, Nolan Mckay, Nalveer Moocheet,Audrey-Laure St-Louis \\
{\bf Where:} H831\\
{\bf Activities:} We  had the demo. Vsevolod Ivanov( coder) presented our team's Kakuro game, MVC and JUnit tests and Nolan Mckay(documenter) explained the documentation \\
{\bf Outcomes:} The TA told the documenters that we are missing some details in out documentation but the codes are well constructed and satisfactory. The coders and the documenters know what to add more and what to change.We assigned tasks to each other and underlined the deliverables with the deadlines. Total time of this week: 6 hours.\\

{\bf Date:} 05 February 2020\\
{\bf Start Time:} 19:15\\
{\bf End Time:} 21:00\\
{\bf Who:} Tiffany Ah King, Isabelle Charette, Brian Gamboc-Javiniar, Vsevolod Ivanov,\\
Chang Liu, Nolan Mckay, Nalveer Moocheet, Hoang Thuan Pham, Audrey-Laure St-Louis, Jia Ming Wei\\
{\bf Where:} H-831\\
{\bf Activities:} We aligned ourself for the submission and the completion of the requirements. As well, we planned the roles for the next iteration.\\
{\bf Outcomes:} Everything is crystal clear and we're on the right track. Total time of this week: 10 hours.\\

{\bf Date:} 06 February 2020\\
{\bf Start Time:} 23:00\\
{\bf End Time:} 01:00\\
{\bf Who:} Tiffany Ah King\\
{\bf Where:} Home\\
{\bf Activities:} I read the "Non-functional Constraints" section of the documentation named "Monopoly phase 1 final" by Team Redmond provided by Greg Butler on his website. I googled some information on what is needed and what I did not understand. I also scrutinized the codes of the Coders from GitHub and I was able to write on it \\
{\bf Outcomes:} The "Non-functional Constraints" section is done and I referenced my work. It still need to be proofread.

{\bf Date:} 07 February 2020\\
{\bf Start Time:} 23:00\\
{\bf End Time:} 00:00 \\
{\bf Who:} Tiffany Ah King\\
{\bf Where:} Home\\
{\bf Activities:} I organized the "Non-functional Constraints" section  because I was not completely satisfied. \\
{\bf Outcomes:} I was able to modify it to my taste and I tried to make it as professional as possible. I asked some help on Discord too. On the 8 February we will have a meeting with all the documenters to have a final check up and to evaluate what is missing.

{\bf Date:} 08 February 2020\\
{\bf Start Time:} 17:00\\
{\bf End Time:} 20:45\\
{\bf Who:} Tiffany Ah King, Brian Gamboc-Javiniar,
Chang Liu, Nolan Mckay, Hoang Thuan Pham\\
{\bf Where:}Home via Discord\\
{\bf Activities:} We went through the document with all the documenters and changes will be applied. \\
{\bf Outcomes:} We have edited the documents and Nolan streamed it\\


{\bf Date:} 08 February 2020\\
{\bf Start Time:} 5:00 PM\\
{\bf End Time:} 7:45 PM \\
{\bf Who:} Tiffany Ah King, Brian Gamboc-Javiniar, Chang Liu, Nolan Mckay, Hoang Thuan Pham\\
{\bf Where:} Home and voice call through discord \\
{\bf Activities:} All the documenters proofread the whole document section by section and we did some modification.
{\bf Outcomes:} We shared our opinions on what needed to be changed. We did some editing while we talked and we had a list of problems that we assigned to each other to work on after the break.\\

{\bf Date:} 08 February 2020\\
{\bf Start Time:} 8:30 PM\\
{\bf End Time:} 11:00 PM \\
{\bf Who:} Tiffany Ah King, Brian Gamboc-Javiniar, Nolan Mckay, Hoang Thuan Pham\\
{\bf Where:} Home and voice call through discord \\
{\bf Activities:} We assigned roles to each problems during the meeting and talked more about what to include or not. \\
{\bf Outcomes:} After communicating our results through Discord, each one of us were able to make all the alteration needed so that we can finalize the document before the QA take over. We also worked on our diary after the call. Total time of this week: 15 hours.\\



%\section{Iteration 2}

%\section{Iteration 3}

\end{document}
