\documentclass[12pt]{article}

\pagestyle{empty}
\setcounter{secnumdepth}{0}

\topmargin=0cm
\oddsidemargin=0cm
\textheight=22.0cm
\textwidth=16cm
\parindent=0cm
\parskip=0.15cm
\topskip=0truecm
\raggedbottom
\abovedisplayskip=3mm
\belowdisplayskip=3mm
\abovedisplayshortskip=0mm
\belowdisplayshortskip=2mm
\normalbaselineskip=12pt
\normalbaselines

\begin{document}

\vspace*{0.2in}
\centerline{\bf\Large Diary}

\vspace*{0.2in}
\centerline{\bf\Large Name: Vsevolod Ivanov   Student ID: 40004286}

\vspace*{0.2in}
\centerline{\bf\Large Team PK-A}

\vspace*{0.2in}
\centerline{\bf\Large 09 January 2020}

\section{Iteration 1}

{\bf Date:} 09 January 2020\\
{\bf Start Time:} 20:15\\
{\bf End Time:} 21:00 \\
{\bf Who:} Tiffany Ah King, Isabelle Charette, Brian Gamboc-Javiniar, Vsevolod Ivanov,\\
Chang Liu, Nolan Mckay, Nalveer Moocheet, Hoang Thuan Pham, Audrey-Laure St-Louis, Jia Ming Wei\\
{\bf Where:} H-920 \\
{\bf Activities:} We met eachother, learned our interests and motivations. Then, we determined and create platforms for communications, kanban and code. We took note of everyone's emails.\\
{\bf Outcomes:} For communnications, we have chosen Discord, for Kanban and User stories Trello or maybe Github and for programming it was GitHub. We fixed the next meeting at the lab Wednesday. Teammates created the Trello and Dicord projects and I created the GitHub repository.\\

{\bf Date:} 15 January 2020\\
{\bf Start Time:} 19:15\\
{\bf End Time:} 22:00\\
{\bf Who:} Tiffany Ah King, Isabelle Charette, Brian Gamboc-Javiniar, Vsevolod Ivanov,\\
Chang Liu, Nolan Mckay, Nalveer Moocheet, Hoang Thuan Pham, Audrey-Laure St-Louis, Jia Ming Wei\\
{\bf Where:} H-831\\
{\bf Activities:} We discovered the project, learned about the roles and iterations. We determined our roles for organiser (1) coders (4) and rest in the documentation! We wrote first user stories brief and assigned coders and documenters for each one to dig deeper into.\\
{\bf Outcomes:} We all have specific but flexible tasks to work / explore more before the next meeting. We started to think in terms of MVC for the architecture of the code. Later that night, I pushed a basic MVC class template for the Game.\\

%\section{Iteration 2}

%\section{Iteration 3}

\end{document}
