\documentclass[12pt]{article}

\pagestyle{empty}
\setcounter{secnumdepth}{0}

\topmargin=0cm
\oddsidemargin=0cm
\textheight=22.0cm
\textwidth=16cm
\parindent=0cm
\parskip=0.15cm
\topskip=0truecm
\raggedbottom
\abovedisplayskip=3mm
\belowdisplayskip=3mm
\abovedisplayshortskip=0mm
\belowdisplayshortskip=2mm
\normalbaselineskip=12pt
\normalbaselines

\begin{document}

\vspace*{0.2in}
\centerline{\bf\Large Diary}

\vspace*{0.2in}
\centerline{\bf\Large Name: Chang Liu Student ID: 40056360}

\vspace*{0.2in}
\centerline{\bf\Large Team PK-A}

\vspace*{0.2in}
\centerline{\bf\Large 15 January 2019}

\section{Iteration 1}

{\bf Date:} 09 January 2020\\
{\bf Start Time:} 8:00 pm\\
{\bf End Time:}  8:40 pm\\
{\bf Who:} Tiffany Ah King, Vsevolod Ivanov, Chang Liu, Nolan Mckay, Nalveer Moocheet, Hoang Thuan Pham, Audrey-Laure St-Louis, Jia Ming Wei\\
{\bf Where:} H920 \\
{\bf Activities:} We get to know each other. We collect each team member's contact information. We discuss to use discord as our communication platform. Basically, we are "linked" each other as a team.\\
{\bf Outcomes:}  We set up a stub of GitHub repository for our team; Our organiser made a team board on Trello. \\\\

{\bf Date:} 15 January 2019\\
{\bf Start Time:} 7.15 pm\\
{\bf End Time:} 8.45 pm \\
{\bf Who:} Chang Liu, Tiffany Ah King, Isabelle Charette, Brian Gamboc-Javiniar, Vsevolod Ivanov, Nolan Mckay, Nalveer Moocheet, Hoang Thuan Pham, Audrey-Laure St-Louis, Jia Ming Wei\\
{\bf Where:} H831 \\
{\bf Activities:} The tutor covers the "programming cycle" --- Planning, Analysis, Design, Implementation, Maintenance. He also mentions about the course objective and the meaning of iteration.\\Group: Discuss the roles and seprerate job
\s.\\ 1. to get to know each other, your semester schedule, work commitments etc;\\2. to discussand agree to roles for iteration 1;\\3. to assign tasks and deadlines for individual team members, especially the Coder assignment to the selected use cases for iteration 1;\\4. plan how Organisers will set up git repository; get everyone’s contact info for communication; plan minutes and diaries;\\
5. discuss the timeline between now and the presentation of iteration 1 in the Laboratory of
Week 4.\\
{\bf Outcomes:} Every one in the group has a role, we have 4 coders, 5 documenters, and 1 organiser; we get to know each other, assign tasks and make targets on github board; discord is the communication application that we vote to use; and we also put the timeline and to do list on github; last but not least, we define the features, MVC, user cases for our project.\\\\


{\bf Date:} 22 January 2019\\
{\bf Start Time:} 7.15 pm\\
{\bf End Time:} 8.45 pm \\
{\bf Who:} Chang Liu, Tiffany Ah King, Isabelle Charette, Brian Gamboc-Javiniar, Vsevolod Ivanov, Nolan Mckay, Nalveer Moocheet, Hoang Thuan Pham, Audrey-Laure St-Louis, Jia Ming Wei\\
{\bf Where:} H831 \\
{\bf Activities:} (Lab: Documenters should review Latex and create a sample document.\\
Coders should review JUnit and create sample unit tests. )\\
1. Resolve any misunderstandings for Iteration 1 about the domain model and use cases;\\
2. Hear how the Coders plan to implement their assigned use case;\\
3. Hear what issues the Documenters have, and what content/information they need; \\
4. Everyone can help create sample data as needed by the unit tests; \\
5. Review the timeline overall for iteration 1, assigned tasks and deadlines.\\
{\bf Outcomes:} We resolve the misunderstandings for Iteration 1, documenters decide to upload the project on the google drive, coders decude to use github to share codes. The main issues for our project are user cases, we are not sure how many user cases we need, and we will confirm with the professor on Thursday's lecture.\\\\



{\bf Date:} 26 January 2019\\
{\bf Start Time:} 7.00 pm\\
{\bf End Time:} 8.00 pm \\
{\bf Who:} Chang Liu,Tiffany King,Brian Gamboc-Javiniar,Nolan Mckay,Hoang Thuan Pham.\\
\
{\bf Where:} Discord channel \\
{\bf Activities:} Solve problems that we meet in our own sections. \\
Discuss how to merge our document on google drive.\\
Talk about the small changes and updates.\\
Set deadline for Wednesday Demo.\\
{\bf Outcomes:} Josh uploads the template for users cases, so everyone in the group can follow the correct format;
Chang and Brain have some questions about the user interface and diagram, we decide leave some questions to confirm with the tutor. We also decide to merge our parts in one google doc, and then translate to Letex language. Our deadline is being set on Tuesday, we have to finish 90 percent for our documentation.\\\\


{\bf Date:} 29 January 2019\\
{\bf Start Time:} 7.15 pm\\
{\bf End Time:} 8.45 pm \\
{\bf Who:} Chang Liu, Tiffany Ah King, Isabelle Charette, Brian Gamboc-Javiniar, Vsevolod Ivanov, Nolan Mckay, Nalveer Moocheet, Audrey-Laure St-Louis\\
{\bf Where:} H831 \\
{\bf Activities:} 
1. Try our best to present the demo and explain the documentation;
2. Learn some knowledge from other groups to make our project perfect;
3. Find the drawbacks that we need to improve; 
4. Discuss what should we do before submitting. \\
{\bf Outcomes:} 
1. Review what needs to be done over the next week to get the application ready for submission; 
2. Documenters need to put more diagrams in their documentation;
3. Coders are ready for submission.\\

{\bf Date:} 05 February 2020\\
{\bf Start Time:} 19:15\\
{\bf End Time:}  21:10\\
{\bf Who:} Tiffany Ah King, Isabelle Charette, Brian Gamboc-Javiniar, Vsevolod Ivanov, Chang Liu, Nolan Mckay, Nalveer Moocheet, Hoang Thuan Pham, Audrey-Laure St-Louis, Jia Ming Wei\\
{\bf Where:} H831 \\
{\bf Activities:}  Documenters discuss how to update the UI diagram in our documentation. Coders review their final code. We decide who submit the code and the documents. We try to make everything perfect.\\
{\bf Outcomes:} There are still some small things need to fix before our submission. We can tell the iteration 1 is almost completed. \\



\end{document}


